Observing Earth as an Exoplanet with \TESS: Photometric Mapping of Surface Features in Reflected Light

### 2019-08-27 tex/ms.tex
typo

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
    \caption{\label{fig:map_temporal}
             The inferred mean map when allowing for slight temporal
             variations in the spherical harmonic coefficients. Compare
             to Figure~\ref{fig:map}. An 3 second animated version of the 
             top panel is available in the HTML version of this article, showing
             the inferred cloud movement during sectors 1 and 2.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

>>>>

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
    \caption{\label{fig:map_temporal}
             The inferred mean map when allowing for slight temporal
             variations in the spherical harmonic coefficients. Compare
             to Figure~\ref{fig:map}. \edited{A 4 second animated version of the 
             top panel is available in the HTML version of this article, showing
             the inferred cloud movement during sectors 1 and 2.}
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}
